Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-17 paper/main.tex
fix format

\subsection{Remote sensing}
NASA's research shows that modern remote sensing technology began with the invention of the camera more than 150 years ago \cite{earthdata28 :online}. The first original photo appeared in the form of a "still image", but it inspired the idea and practice of people taking pictures and looking down on the surface of the earth. This idea appeared in the 1840s. The first photo was used for topographic mapping. At the end of the First World War, the cameras installed on the aircraft provided a bird's-eye view of a considerable area and provided a large amount of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached a qualitative leap.

Remote sensing technology is usually used to describe objects, without direct contact, only to identify, observe and measure. Most of the data in this project comes from the detection and measurement of radiation of different wavelengths reflected or emitted from distant objects or materials. Through these radiations, they can be identified and classified by category, substance and spatial distribution\cite{earthdata28 :online}Finally determine the wavelength of the light to image.

@@

Polar orbiting satellites (picture ~\ref{satellites}) have an orbit close to 90 degrees to the equator. This angle allows the satellite to better perceive and observe the earth, so that more data can be collected more simply and in detail. Including polar regions and some areas where it is difficult to collect data\WhatisRe36:online}. Most of the NOAA polar satellites mentioned in the project provide infrared and visible light earth image data. Sometimes they also collect some data on the atmosphere\cite{side357:online}. Most polar-orbiting satellites are sun-synchronous. This is to allow the satellites to pass the same position at the same solar time in each cycle. Such satellites will also reach the Antarctic and North Pole in different orbits to collect meteorological, ocean, land, climate and other professional data.

@@

For example: this is a file from database called F12199501010014.night.OIS， and lots of information will be given to this file.

@@

The file example of data is called: 
SVDNB\_npp\_d20150504\_t1335358\_e13411
62\_b18219\_c20150504194116381040\_noaa
\_ops.rade9.co.tif. The file structure is:
Then there are lots details about what them are.
\begin{itemize}
    \item npp\_d20150504\_t1335358\_e1341162\_b18219
    \item npp = satellite ID
    \item d20150504 = start date of first scan in aggregate \\
    (2015/05/04)
    \item t1335358 = time of first scan (13:35:35.8)
    \item e1341162 = time of last scan (13:41:16.2)
    \item b18219 = orbit number of first scan
\end{itemize}

>>>>

\subsection{Remote sensing}
NASA's research shows that modern remote sensing technology began with the invention of the camera more than 150 years ago \cite{earthdata28:online}. The first original photo appeared in the form of a "still image", but it inspired the idea and practice of people taking pictures and looking down on the surface of the earth. This idea appeared in the 1840s. The first photo was used for topographic mapping. At the end of the First World War, the cameras installed on the aircraft provided a bird's-eye view of a considerable area and provided a large amount of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached a qualitative leap.

Remote sensing technology is usually used to describe objects, without direct contact, only to identify, observe and measure. Most of the data in this project comes from the detection and measurement of radiation of different wavelengths reflected or emitted from distant objects or materials. Through these radiations, they can be identified and classified by category, substance and spatial distribution\cite{earthdata28:online}Finally determine the wavelength of the light to image.

@@

Polar orbiting satellites (picture ~\ref{satellites}) have an orbit close to 90 degrees to the equator. This angle allows the satellite to better perceive and observe the earth, so that more data can be collected more simply and in detail. Including polar regions and some areas where it is difficult to collect data\cite{WhatisRe36:online}. Most of the NOAA polar satellites mentioned in the project provide infrared and visible light earth image data. Sometimes they also collect some data on the atmosphere\cite{side357:online}. Most polar-orbiting satellites are sun-synchronous. This is to allow the satellites to pass the same position at the same solar time in each cycle. Such satellites will also reach the Antarctic and North Pole in different orbits to collect meteorological, ocean, land, climate and other professional data.

@@

For example: this is a file from database called \\F12199501010014.night.OIS, and lots of information will be given to this file.

@@

The file example of data is called: SVDNB\_npp\_d201505\\04\_t1335358\_e1341162\_b18219\_c20150504194116381040\_\\noaa\_ops.rade9.co.tif. 
The file structure is:
Then there are lots details about what them are.
\begin{itemize}
    \item npp\_d20150504\_t1335358\_e1341162\_b18219
    \item npp = satellite ID
    \item d20150504 = start date of first scan in aggregate \\
    (2015/05/04)
    \item t1335358 = time of first scan (13:35:35.8)
    \item e1341162 = time of last scan (13:41:16.2)
    \item b18219 = orbit number of first scan
\end{itemize}
